Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2021-09-24 methods_paper/fabl-paper.tex
more writing.

\subsection{Fellegi-Sunter Model}

>>>>

\subsection{Fellegi-Sunter Model}
In this section, we review the Fellegi-Sunter model. While we have introduced comparison data, $\bm{\gamma}_{ij}$, this is not sufficient to determine whether a record is a match/non-match given errors that naturally occur in the data. This motivated \cite{fellegi_theory_1969} to consider the following likelihood ratio
\begin{align}
w_{ij} = \log \frac{P(\gamma_{ij} \mid \Delta_{ij} = 1)}{P(\gamma_{ij} \mid \Delta_{ij} = 0)}
\end{align}
as a weight to estimate if record pairs were a match/non-match.
